\vspace{-2.5em} Singular value decomposition of single view\\ polarized fluorescence microscopes\vspace{-1em}

### 2018-05-17 notes/2018-05-14-single-view-continuous-svd/report/report.tex
Update continuous single view notes.

\subsection{Kernel}
In previous notes we showed that the excitation point response function for
unpolarized epi-illumination is given by
\begin{align}
  h_{\text{exc}}^{\mh{z}}(\so{}) = h_{\text{exc},0,0}^0y_0^0(\so{}) + h_{\text{exc},0,0}^2y_2^0(\so{}).
\end{align}
where
\begin{align}
  h_{\text{exc},0,0}^0 &= 1,\\
  h_{\text{exc},0,0}^2 &= -\frac{1}{\sqrt{5}}\tilde{A}.
\end{align}

We also showed that the point response function for polarized detection is given
by (rewritten in terms of the circular harmonics)
\begin{align}
  h_{\text{det}}(\ro{}, \so{}; \mh{p}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{\text{det},l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
\end{align}
where
\begin{align}
  h_{\text{det},0,0}^0(\ro{}) &= a^2(r_o) + 2b^2(r_0),\\
  h_{\text{det},0,-2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{-2}(\ro{}),\\
  h_{\text{det},0,2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{2}(\ro{}),\\
  h_{\text{det},2,0}^0(\ro{}) &= \frac{1}{\sqrt{5}}\left[-a^2(r_o) + 4b^2(r_0)\right],\\
  h_{\text{det},2,-2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{-2}(\ro{}),\\
  h_{\text{det},2,2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{2}(\ro{}),\\
  h_{\text{det},2,2}^2(\ro{}) &= -h_{\text{det},2,2}^{-2}(\ro{}) = \sqrt{\frac{3}{5}}a^2(r_o).
\end{align}
The complete kernel for unpolarized illumination and polarized detection is given by
\begin{align}
  h(\ro{}, \so{}; \mh{p}_d) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
\end{align}
where
\begin{align}
  h_{0,0}^0(\ro{}) &= h_{\text{exc},0,0}^0h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{})\\
  h_{0,-2}^0(\ro{}) &= h_{\text{exc},0,-2}^0h_{\text{det},0,-2}^0(\ro{}) + h_{\text{exc},2,-2}^0h_{\text{det},2,-2}^0(\ro{})\\
  h_{0,2}^0(\ro{}) &= h_{\text{exc},0,2}^0h_{\text{det},0,2}^0(\ro{}) + h_{\text{exc},2,2}^0h_{\text{det},2,2}^0(\ro{})\\
  h_{2,0}^0(\ro{}) &= \\
  h_{2,-2}^0(\ro{}) &= \\
  h_{2,2}^0(\ro{}) &= \\
  h_{2,2}^2(\ro{}) &= -h_{\text{det},2,2}^{-2}(\ro{}) = .
\end{align}

% [h00d*h00e + h20d*h20e, h2_2d*(7*h00e - 2*sqrt(5)*h20e)/7, 0, h00d*h20e + h00e*h20d + 2*sqrt(5)*h20d*h20e/7, 0, h22d*(7*h00e - 2*sqrt(5)*h20e)/7, 0, 0, sqrt(15)*h20e*h2_2d/7, 0, 6*h20d*h20e/7, 0, sqrt(15)*h20e*h22d/7, 0, 0]
\begin{align}
  h_{0,0}^0(\ro{}; \mh{p}_d) = a^2(r_o) + 2b^2(r_o)[1 + z_{-2}(\ro{})z_{-2}(\mh{p}_d) + z_{2}(\ro{})z_{2}(\mh{p}_d)]
\end{align}

\subsection{Transfer function}
\subsection{Singular value decomposition}

>>>>

\subsection{Kernel}
In previous notes we showed that the excitation point response function for
unpolarized epi-illumination is given by
\begin{align}
  h_{\text{exc}}^{\mh{z}}(\so{}) = h_{\text{exc},0,0}^0y_0^0(\so{}) + h_{\text{exc},0,0}^2y_2^0(\so{}).
\end{align}
where
\begin{align}
  h_{\text{exc},0,0}^0 &= 1,\\
  h_{\text{exc},2,0}^0 &= -\frac{1}{\sqrt{5}}\tilde{A}.
\end{align}

We also showed that the point response function for polarized detection is given
by (rewritten in terms of the circular harmonics)
\begin{align}
  h_{\text{det}}(\ro{}, \so{}; \mh{p}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{\text{det},l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
\end{align}
where
\begin{align}
  h_{\text{det},0,0}^0(\ro{}) &= a^2(r_o) + 2b^2(r_0),\\
  h_{\text{det},0,\pm 2}^0(\ro{}) &= 2\sqrt{\pi} b^2(r_0)z_{\pm 2}(\ro{}),\\
  h_{\text{det},2,0}^0(\ro{}) &= \frac{1}{\sqrt{5}}\left[-a^2(r_o) + 4b^2(r_0)\right],\\
  h_{\text{det},2,\pm 2}^0(\ro{}) &= 4\sqrt{\frac{\pi}{5}}b^2(r_0)z_{\pm 2}(\ro{}),\\
  h_{\text{det},2,2}^2(\ro{}) &= -h_{\text{det},2,-2}^{-2}(\ro{}) = \sqrt{\frac{3}{5}}a^2(r_o).
\end{align}
The complete kernel for unpolarized illumination and polarized detection is given by
\begin{align}
  h(\ro{}, \so{}; \mh{p}_d) = h_{\text{exc}}(\so{})h_{\text{det}}(\ro{}, \so{}; \mh{p}_d) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} h_{l,n}^m(\ro{})y_l^m(\so{})z_n(\mh{p}_d), 
\end{align}
where
\begin{align}
  h_{0,0}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,0}^0(\ro{}),\\
  h_{0,\pm 2}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,\pm 2}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,\pm 2}^0(\ro{}),\\
  h_{2,0}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,0}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,0}^0(\ro{}) + \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{}),\\
  h_{2,\pm 2}^0(\ro{}) &= h_{\text{exc},0,0}^0 h_{\text{det},0,\pm 2}^0(\ro{}) + h_{\text{exc},2,0}^0 h_{\text{det},2,\pm 2}^0(\ro{}) + \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^0(\ro{}),\\
  h_{2,\pm 2}^{\pm 2}(\ro{}) &= h_{\text{det},2,\pm 2}^{\pm 2}(\ro{})\left[h_{\text{exc},0,0}^0 - \frac{2\sqrt{5}}{7}h_{\text{exc},2,0}^0\right],\\
  h_{4,0}^0(\ro{}) &= \frac{6}{7}h_{\text{exc},2,0}^0h_{\text{det},2,0}^0(\ro{}),\\
  h_{4,\pm 2}^0(\ro{}) &= \frac{6}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^0(\ro{}),\\
  h_{4,\pm 2}^{\pm 2}(\ro{}) &= \frac{\sqrt{15}}{7}h_{\text{exc},2,0}^0h_{\text{det},2,\pm 2}^{\pm 2}(\ro{}),
\end{align}
% hh0
% [h000d*h000e + h200d*h200e, 0, 0, h000d*h200e + h000e*h200d + 2*sqrt(5)*h200d*h200e/7, 0, 0, 0, 0, 0, 0, 6*h200d*h200e/7, 0, 0, 0, 0]

% hh2
% [h000e*h002d + h200e*h202d, 0, 0, h000e*h202d + h002d*h200e + 2*sqrt(5)*h200e*h202d/7, 0, h222d*(7*h000e - 2*sqrt(5)*h200e)/7, 0, 0, 0, 0, 6*h200e*h202d/7, 0, sqrt(15)*h200e*h222d/7, 0, 0]

% hh_2
% [h000e*h00_2d + h200e*h20_2d, h2_2_2d*(7*h000e - 2*sqrt(5)*h200e)/7, 0, h000e*h20_2d + h00_2d*h200e + 2*sqrt(5)*h200e*h20_2d/7, 0, 0, 0, 0, sqrt(15)*h200e*h2_2_2d/7, 0, 6*h200e*h20_2d/7, 0, 0, 0, 0]
and the remaining terms in the series are zero. Plugging in the excitation and
detection point response functions gives the following
\begin{align}
  h_{0,0}^0(\ro{}) &= \left[\frac{\tilde{A}}{5} + 1\right]a^2(r_o) + \left[-\frac{4\tilde{A}}{5} + 2\right]b^2(r_o),\\ 
  h_{0,\pm 2}^0(\ro{}) &= 2\sqrt{\pi}\left[1 - \frac{2\tilde{A}}{5}\right]b^2(r_o)z_{\pm 2}(\ro{}),\\ 
  h_{2,0}^0(\ro{}) &= \frac{\sqrt{5}}{35}\left\{-\left[5\tilde{A} + 7\right]a^2(r_o) + \left[-22\tilde{A} + 28\right]b^2(r_0)\right\},\\ 
  h_{2,\pm 2}^0(\ro{}) &= \frac{2\sqrt{5\pi}}{35}\left[-11\tilde{A} + 14\right]b^2(r_o)z_{\pm 2}(\ro{})\\ 
  h_{2,2}^{2}(\ro{}) &= h_{2,-2}^{-2}(\ro{}) = \frac{\sqrt{15}}{5}\left[\frac{2\tilde{A}}{7} + 1\right]a^2(r_o),\\ 
  h_{4,0}^0(\ro{}) &= \frac{6\tilde{A}}{35}\left[a^2(r_o) - 4b^2(r_o)\right],\\ 
  h_{4,\pm 2}^0(\ro{}) &= -\frac{24\sqrt{\pi}}{35}\tilde{A}b^2(r_o)z_{\pm 2}(\ro{}),\\ 
  h_{4,2}^{2}(\ro{}) &= h_{4,-2}^{-2}(\ro{}) = -\frac{3\sqrt{5}}{35}\tilde{A}a^2(r_o). 
\end{align}
% hh0
% [At*(a - 4*b)/5 + a + 2*b, 0, 0, sqrt(5)*(-5*At*a - 22*At*b - 7*a + 28*b)/35, 0, 0, 0, 0, 0, 0, 6*At*(a - 4*b)/35, 0, 0, 0, 0]

% hh2
% [2*sqrt(pi)*b*z2*(-2*At + 5)/5, 0, 0, 2*sqrt(5)*sqrt(pi)*b*z2*(-11*At + 14)/35, 0, a*(2*sqrt(15)*At/35 + sqrt(15)/5), 0, 0, 0, 0, -24*sqrt(pi)*At*b*z2/35, 0, -sqrt(15)*sqrt(3)*At*a/35, 0, 0]

% hh_2
% [2*sqrt(pi)*b*z_2*(-2*At + 5)/5, a*(0.221313334068995*At + 0.774596669241483), 0, 2*sqrt(5)*sqrt(pi)*b*z_2*(-11*At + 14)/35, 0, 0, 0, 0, -0.110656667034498*sqrt(3)*At*a, 0, -24*sqrt(pi)*At*b*z_2/35, 0, 0, 0, 0]

\subsection{Transfer function}
The transfer function for unpolarized illumination and polarized detection is
given by
\begin{align}
  H_{l,n}^m(\bs{\nu}) = \sum_{l=0}^{\infty}\sum_{m=-l}^l\sum_{n=-\infty}^{\infty} H_{l,n}^m(\bs{\nu})\delta_{ll'}\delta_{mm'}\delta_{nn'},
\end{align}
where
\begin{align}
  H_{0,0}^0(\bs{\nu}) &= \left[\frac{\tilde{A}}{5} + 1\right]A(\nu) + \left[-\frac{4\tilde{A}}{5} + 2\right]B(\nu),\\ 
  H_{0,\pm 2}^0(\bs{\nu}) &= 2\sqrt{\pi}\left[1 - \frac{2\tilde{A}}{5}\right]C(\nu)z_{\pm 2}(\bs{\nu}),\\ 
  H_{2,0}^0(\bs{\nu}) &= \frac{\sqrt{5}}{35}\left\{-\left[5\tilde{A} + 7\right]A(\nu) + \left[-22\tilde{A} + 28\right]B(r_0)\right\},\\ 
  H_{2,\pm 2}^0(\bs{\nu}) &= \frac{2\sqrt{5\pi}}{35}\left[-11\tilde{A} + 14\right]C(\nu)z_{\pm 2}(\bs{\nu})\\ 
  H_{2,2}^{2}(\bs{\nu}) &= H_{2,-2}^{-2}(\bs{\nu}) = \frac{\sqrt{15}}{5}\left[\frac{2\tilde{A}}{7} + 1\right]A(\nu),\\ 
  H_{4,0}^0(\bs{\nu}) &= \frac{6\tilde{A}}{35}\left[A(\nu) - 4B(\nu)\right],\\ 
  H_{4,\pm 2}^0(\bs{\nu}) &= -\frac{24\sqrt{\pi}}{35}\tilde{A}C(\nu)z_{\pm 2}(\bs{\nu}),\\ 
  H_{4,2}^{2}(\bs{\nu}) &= H_{4,-2}^{-2}(\bs{\nu}) = -\frac{3\sqrt{5}}{35}\tilde{A}A(\nu). 
\end{align}
where 
\begin{align}
  A(\nu) &= \frac{2}{\pi}\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \frac{\nu}{2\nu_o}\sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  B(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[\arccos\left(\frac{\nu}{2\nu_o}\right) - \left[3 - 2\left(\frac{\nu}{2\nu_o}\right)^2\right]\frac{\nu}{2\nu_o} \sqrt{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right),\\
  C(\nu) &= \frac{1}{\pi}\left(\frac{\text{NA}}{n_o}\right)^2\left[-\frac{4}{3}\frac{\nu}{2\nu_o}\sqrt[3]{1 - \left(\frac{\nu}{2\nu_o}\right)^2}\right]\Pi\left(\frac{\nu}{2\nu_o}\right).
\end{align}

\subsection{Singular value decomposition}
We follow the same procedure and plug the transfer function into the
frequency-domain eigenvalue problem (Eq. \ref{eq:freqsvd}) which gives a
$3\times 3$ eigenvalue problem
\begin{align}
  \mathsf{K}\mathsf{V}_j &= \mu_{j}\mathsf{V}_j,
\end{align}
where the entries of $\mathsf{K}$ are given by
\begin{align}
  \mathsf{K}_{00} &= \sum_{l,m}H_{l,-2}^{m}H_{l,-2}^{m} = \{H_{0,-2}^{0}\}^2 + \{H_{2,-2}^{-2}\}^2 + \{H_{2,-2}^{0}\}^2 + \{H_{4,-2}^{-2}\}^2 + \{H_{4,-2}^{0}\}^2,\\
  \mathsf{K}_{11} &= \sum_{l,m}H_{l,0}^{m}H_{l,0}^{m} = \{H_{0,0}^{0}\}^2 + \{H_{2,0}^{0}\}^2 + \{H_{4,0}^{0}\}^2,\\
  \mathsf{K}_{22} &= \sum_{l,m}H_{l,2}^{m}H_{l,2}^{m} = \{H_{0,2}^{0}\}^2 + \{H_{2,2}^{2}\}^2 + \{H_{2,2}^{0}\}^2 + \{H_{4,2}^{2}\}^2 + \{H_{4,2}^{0}\}^2,\\
  \mathsf{K}_{01} &= \mathsf{K}_{10} = \sum_{l,m}H_{l,-2}^{m}H_{l,0}^{m} = H_{0,-2}^{0}H_{0,0}^{0} + H_{2,-2}^{0}H_{2,0}^{0} + H_{4,-2}^{0}H_{4,0}^{0},\\
  \mathsf{K}_{02} &= \mathsf{K}_{20} = \sum_{l,m}H_{l,-2}^{m}H_{l,2}^{m} = H_{0,-2}^{0}H_{0,2}^{0} + H_{2,-2}^{0}H_{2,2}^{0} + H_{4,-2}^{0}H_{4,2}^{0},\\
  \mathsf{K}_{12} &= \mathsf{K}_{21} = \sum_{l,m}H_{l,0}^{m}H_{l,2}^{m} = H_{0,0}^{0}H_{0,2}^{0} + H_{2,0}^{0}H_{2,2}^{0} + H_{4,0}^{0}H_{4,2}^{0}.
\end{align}
The eigenvalues and eigenvectors can be computed in a closed form (and I've done
this using a symbolic package), but writing the result would fill several pages
with notation and provide little insight. Instead we proceed straight to plots
of the eigenvalues and eigenvectors shown in Fig. XXX.
